\LARGE \bf Analysis of the effectiveness of recursive networks in the classification task

### 2019-06-12 paper/main.tex
paper: Introduction added

@@

@@

We can utilize mapping defined by Hilbert Curve to reduce dimensionality of image. Then we can reduce number of recurrent neural networks in each ReNet layer. Instead of 4 RNN swapping image columns and rows we can introduce 2 RNN swaping image converted to 1D sequence with Hilbert Curve.

@@

Based on the qualitative results one can say, that convulutional neural networks achieve better accuracy then ReNet and ReNet with modfication. In 3 out of 4 used datasets modified ReNet obtained similar or better results then ReNet. In for Natural Images dataset ReNet outperformes ReNet with modification. For the last dataset some issues were observed and 7 layers of ReNet with modification were need. This shows, that modification introduced in this paper is applicable to all datasets. Introducing modification yielded in substantial speedup for the same datasets, where no performance decrease was noted.

@@

One may ask if speedup obtained is sufficient to provide more practical use for ReNet networks. In case of this studies convolutional networks still obtain better results. Further research in order to improve accuracy and reduce training time of ReNet are required.

Code used for perforing tests is avaliable online in \cite{repo}.

>>>>

\begin{keywords}
Neural networks, image recognition, image classification, recurrent neural networks.
\end{keywords}
%\articleinfobox

@@

Feedforward neural networks have fix amount of inputs and outputs. This can be quite challenging limitation when processing sequences. For example sentence can have 5 words or it can have 9 words. For processing sequences with neural models Recurrent Neural Networks (RNN) \cite{RNN} were developed. In this models a hidden state was introduced, so the network could update state at each time step based on previous state and actual input. RNNs are learned with backpropagation in time algorithm \cite{BPTT}. Two most noticable modification of basic RNN structure are Long Short-Term Memory (LSTM) \cite{LSTM} and Gated Recurrent Unit (GRU) \cite{DBLP:journals/corr/ChoMGBSB14}. Both of them are able to learn long term dependencies in data across many timesteps.

Most common areas of application of RNNs are natural language processing, recognition of handwriting and generation of text, music or images. In this work we will focus on ReNet architecture \cite{DBLP:journals/corr/VisinKCMCB15}, that tackles image classification task with RNNs. Modification to ReNet layer was introduced, aimed at reducing traning time. Also comparison of ReNet networks with convolutional networks was performed.

@@

We can utilize mapping defined by Hilbert Curve to reduce dimensionality of image. By doing so we reduce number of recurrent neural networks in each ReNet layer. Instead of 4 RNN swapping image columns and rows we can introduce 2 RNN swaping image converted to 1D sequence with Hilbert Curve.

@@

Based on the qualitative results one can say, that convulutional neural networks achieve better accuracy then ReNet and ReNet with modfication. In 3 out of 4 used datasets modified ReNet obtained similar or better results then ReNet. For Natural Images dataset ReNet outperformes ReNet with modification. For the last dataset some issues were observed and 7 layers of ReNet with modification were need. This shows, that modification introduced in this paper is applicable to all datasets. Introducing modification yielded in substantial speedup for the same datasets, where no performance decrease was noted.

@@

One may ask if obtained speedup is sufficient to provide more practical use for ReNet networks. Is ReNet really a valid alternative to convolutional networks for practitioners and researchers? Based on results of this study we can say, that convolutional networks still obtain better accuracy and lower training time. Further research in order to improve accuracy and reduce training time of ReNet are required.

Code with models used for performnig tests is avaliable online in \cite{repo}.
